A saturation model for impaired learning with enhanced plasticity

### 2013-07-12 MHCslides/MHCslides.tex
typos

\begin{frame}{Vestibular Occular Reflex}
%
 \parbox[t]{0.4\linewidth}{\aligntop{\includegraphics[width=0.99\linewidth]{VOR.svg}}}
 \parbox[t]{0.59\linewidth}{%
 Eye movements compensate for head movements to maintain fixation.

@@

\begin{frame}{MHC-I D$^\mathrm{b}$K$^\mathrm{b} -/-$ knockout}
%
 Knockout of molecule lowers threshold for LTD in PF-Pk synapses.\\
 \citerr{McConnell2009MHCcerebellum}
 \note[item]{Easier LTD \lto expect better learning}

@@

\begin{frame}{Saturation hypothesis}
%
 \begin{center}
 \begin{tabular}{ccc}
   Error model & \hspace{0.1\linewidth} & Saturation model \\[1cm]
   \alignmid{\includegraphics[width=0.3\linewidth]{err_model.svg}} &&
   \alignmid{\includegraphics[width=0.3\linewidth]{sat_model.svg}}
 \end{tabular}
 \end{center}
 \note[item]{Older explanation: error model}
 \note[item]{Our model: baseline activity \lto saturation \lto less depression possible}
%
\end{frame}

@@

\begin{frame}{Summary of training results}
%
 \begin{center}
   \alignmid{\includegraphics[width=0.6\linewidth]{data_shifted.svg}}
   \hspace{0.05\linewidth}
   \alignmid{\includegraphics[width=0.3\linewidth]{comparisons.svg}}
 \end{center}
 \note[item]{Restricted to gain inc for comparison}
 \note[item]{Black: WT. Red: KO}
 \note[item]{Solid: no pre. Dashed: with pre}
 \note[item]{Horz and vert comparisons: conceptual}
 \note[item]{Diagonal comparisons: paramter fitting. Depend on size of KO vs.\ pretraining}
 \note[item]{KO hurts w/o, but helps w/}
 \note[item]{pre helps KO but hurts WT}
 \note[item]{top and left most restrictive}
%
\end{frame}

>>>>

\begin{frame}{Vestibulo-Occular Reflex}
%
 \parbox[t]{0.4\linewidth}{\aligntop{\includegraphics[width=0.99\linewidth]{VOR.svg}}}
 \parbox[t]{0.59\linewidth}{%
 Eye movements compensate for head movements to maintain fixation.

@@

\begin{frame}{MHC-I D$^\mathrm{b}$K$^\mathrm{b} -/-$ knockout}
%
 Knockout of molecules lowers threshold for LTD in PF-Pk synapses.\\
 \citerr{McConnell2009MHCcerebellum}
 \note[item]{Easier LTD \lto expect better learning}

@@

\begin{frame}{Viral rescue removes defect}
%
 Local injection of Pk specific virus used to restore the knocked-out molecules.

 \vp\begin{center}
   \alignmid{\includegraphics[width=0.3\linewidth]{rescue.svg}}
   \hspace{0.1\linewidth}
   \alignmid{\includegraphics[width=0.5\linewidth]{rescue_results.svg}}
 \end{center}
 \note[item]{removes defect}
 \note[item]{tells us that it is these PF-Pk synapses that are important}
 \note[item]{But what mechanism?}
%
\end{frame}

\begin{frame}{Saturation hypothesis}
%
 \begin{center}
 \begin{tabular}{ccc}
   Error model & \hspace{0.1\linewidth} & Saturation model \\[1cm]
   \alignmid{\includegraphics[width=0.3\linewidth]{err_model.svg}} &&
   \alignmid{\includegraphics[width=0.3\linewidth]{sat_model.svg}}
 \end{tabular}
 \end{center}
 \note[item]{Older explanation: error model}
 \note[item]{Our model: baseline activity \lto saturation \lto less depression possible}
 \note[item]{Saturation has to compete with enhanced plsaticity. Which will win?}
%
\end{frame}

@@

\begin{frame}{Summary of training results}
%
 \begin{center}
   \alignmid{\includegraphics[width=0.6\linewidth]{data_shifted.svg}}
   \hspace{0.05\linewidth}
   \alignmid{\includegraphics[width=0.3\linewidth]{comparisons.svg}}
 \end{center}
 \note[item]{Restricted to gain inc for comparison}
 \note[item]{Black: WT. Red: KO}
 \note[item]{Solid: no pre. Dashed: with pre}
 \note[item]{Horz and vert comparisons: conceptual}
 \note[item]{Diagonal comparisons: paramter fitting. Depend on size of KO vs.\ pretraining}
 \note[item]{KO hurts w/o, but helps w/}
 \note[item]{pre helps KO but hurts WT}
 \note[item]{top and left most restrictive}
 \note[item]{Pay attention to solid: black above red}
 \note[item]{Pay attention to black: solid above dashed}
 \note[item]{Concentrate on initial slope}
%
\end{frame}
